Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A cross-sectional study based on the parametric g-formula

### 2024-08-12 output/paper/_figures.qmd
Combining forest plots of RQ3 and RQ3SA.

  # From table of numerical results to ggplot object
  tbl_num_res <- obj$numerical_results |>
    dplyr::bind_rows(
      tibble::tibble(
        variable = "Exposure",
        val = "Marginal contrast (95% CI)",
        estimate = 100,
        outcome = "",
        class = "AAA",
        modifier = c(NA, NA, NA)
      ),
      tbl_num_res
    ) |>
    dplyr::group_by(class) |>
    dplyr::arrange(
      variable,
      .by_group = TRUE
    ) |>
    dplyr::ungroup() |>
    dplyr::mutate(
      variable = factor(variable, levels = unique(variable)),
      variable = forcats::fct_rev(variable)
    ) |>
    tidylog::select(-estimate) |>
    ggplot2::ggplot(
      ggplot2::aes(
        y = variable,
        shape = modifier
      )
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 0,
        label = variable
      ),
      hjust = 0,
      fontface = "bold"
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 1,
        label = val
      ),
      hjust = 0,
      position = ggstance::position_dodgev(height = 0.9)
    ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      strip.background = ggplot2::element_blank(),
      strip.text = ggplot2::element_blank(),
      legend.position = "bottom",
      legend.box = "vertical",
      legend.margin = ggplot2::margin()
    ) +
    ggplot2::coord_cartesian(
      xlim = c(0, 4)
    )

>>>>

  # From table of numerical results to ggplot object
  tbl_num_res <- obj$numerical_results |>
    dplyr::bind_rows(
      tibble::tibble(
        variable = "Exposure",
        val = "Marginal contrast (95% CI)",
        estimate = 100,
        outcome = "",
        class = "AAA",
        modifier = c(NA, NA, NA)
      ),
      obj$numerical_results
    ) |>
    dplyr::group_by(class) |>
    dplyr::arrange(
      variable,
      .by_group = TRUE
    ) |>
    dplyr::ungroup() |>
    dplyr::mutate(
      variable = factor(variable, levels = unique(variable)),
      variable = forcats::fct_rev(variable)
    ) |>
    tidylog::select(-estimate) |>
    ggplot2::ggplot(
      ggplot2::aes(
        y = variable,
        shape = modifier
      )
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 0,
        label = variable
      ),
      hjust = 0,
      fontface = "bold"
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 1,
        label = val
      ),
      hjust = 0,
      position = ggstance::position_dodgev(height = 0.9)
    ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      strip.background = ggplot2::element_blank(),
      strip.text = ggplot2::element_blank(),
      legend.position = "bottom",
      legend.box = "vertical",
      legend.margin = ggplot2::margin()
    ) +
    ggplot2::coord_cartesian(
      xlim = c(0, 4)
    )
